Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-03-30 Experiments.tex
Added Answers to Matteo's questions and  refinement of Experiments

Experiments % consist in running
run instances of AthenaMP by using NGE pilots, % where each AthenaMP simulates
simulating a pre-determined number of events in the ATLAS detector.\mtnote{are
they 100 events?}
% taken from ATLAS workload.
We present three groups of experiments in which we test the NGE for weak
scalability, weak scalability with multiple generation, and strong scalability.

@@

% The
In this experiment % consists in running
we run as many AthenaMP instances (also referred as tasks from now-on) as the number of nodes controlled by the pilot. Each AthenaMP
% have been assigned with 100 events whose simulation requires
simulates 100 events, requiring ~$70$ minutes.

@@

This experiment is similar to the one presented above but, in this case, we want
to test also the impact of submitting multiple generations of % new
AthenaMP to the same pilot.\mtnote{we used `generations' at the beginning of 6,
I am assuming the reader understands the term by now. Please change if you
disagree.}
% instances in place of those that end.
% The reason behind this experiment is to
In this way, we stress the pilot's components, % by pushing new tasks while others are ending their execution
as new tasks are scheduled for execution on the Agent while other tasks are still running.

In order to perform the experiments in less than 2 hours per run\mtnote{we do
we need to keep it below 2 hours?}, we
% decided to send for execution a number of AthenaMP instances equal to
used five times AthenaMP instances than the number of worker nodes. % and w
We also reduced  the number of events
% that are simulated
simulated by each AthenaMP to sixteen.
% \footnote{Note that the number of events has been chosen in such a way
% that all the cores of a node run one event.}
In this way, every core of each worker node was used to simulate one event,
%. This allows us to complete
reducing the running time of each AthenaMP to ~$20$ minutes. % only.

We tested
% different
pilots
% sizes, i.e. :
with 256, 512, 1024 and 2048 worker nodes and
%. For all of them, the walltime was
3\mtnote{2?} hours walltime. Figure~\ref{fig:weakScal2a} depicts the average
pilot duration, the average execution time of five sequential
instances\mtnote{generations?} of AthenaMP, and the corresponding overhead. We
% can
observe that the difference between the two durations is more marked than in the
previous experiments \mtnote{mostly due to the increased overhead?}. Despite
this, we
% can
notice that the growth of the overhead is still less than linear.

@@

The last experiments % deals with
study strong scalability. % Therefore, we
by running the same amount of tasks for different pilot sizes. We used
% a number of AthenaMP instances equal to
2048 AthenaMP instances and % tested
pilots with 256, 512, 1024 and 2048 nodes. Thus, the number of sequential
AthenaMP instances is equal to 8 for the smallest pilot and is null for the
largest\mtnote{Not sure I understand this sentence}. Each AthenaMP instance
simulates sixteen events as in the previous experiment.

>>>>

Experiments % consist in running
run instances of AthenaMP by using NGE pilots, % where each AthenaMP simulates
simulating a pre-determined number of events in the ATLAS detector.\mtnote{are
they 100 events?}\aanote{`Not always.'}
% taken from ATLAS workload.
We present three groups of experiments in which we test the NGE for weak
scalability, weak scalability with multiple generation, and strong scalability.

@@

% The
In this experiment % consists in running
we run as many AthenaMP instances (also referred as tasks from now-on) as the number of nodes controlled by the pilot. Each AthenaMP
% have been assigned with 100 events whose simulation requires
simulates 100 events, requiring $\sim 70$ minutes on average.

@@

This experiment is similar to the one presented above but, in this case, we want
to test also the impact of submitting multiple generations of % new
AthenaMP to the same pilot.\mtnote{we used `generations' at the beginning of 6,
I am assuming the reader understands the term by now. Please change if you
disagree.}\aanote{I agree}
% instances in place of those that end.
% The reason behind this experiment is to
In this way, we stress the pilot's components, % by pushing new tasks while others are ending their execution
as new tasks are scheduled for execution on the Agent while other tasks are still running.

\mtnote{we do
we need to keep it below 2 hours?}\aanote{You are right. It was misleadind. I Changed. Check if you like it.}
% decided to send for execution a number of AthenaMP instances equal to
We performed the experiment by running five AthenaMP instances per node. % and w
Since we are focusing on the overhead generated by the scheduling and bootstrap of AthenaMP instances, we also reduced  the number of events simulated by each AthenaMP to sixteen in such a way that the running time of each AthenaMP is, on average, $\sim 20$ minutes.
This choice has been made to avoid the wasting of Titan's core hours but it does not affect the aim of the experiment.  
% \footnote{Note that the number of events has been chosen in such a way
% that all the cores of a node run one event.}
%In this way, every core of each worker node was used to simulate one event,
%. This allows us to complete
%reducing the running time of each AthenaMP to ~$20$ minutes. % only.

We tested
% different
pilots
% sizes, i.e. :
with 256, 512, 1024 and 2048 worker nodes and
%. For all of them, the walltime was
3\mtnote{2?} hours walltime. Figure~\ref{fig:weakScal2a} depicts the average
pilot duration, the average execution time of five sequential
generations\mtnote{generations?}\aanote{Changed} of AthenaMP, and the corresponding overhead. We
% can
observe that the difference between the two durations is more marked than in the
previous experiments \mtnote{mostly due to the increased overhead?}\aanote{Well, I guess that's plain.}. Despite this, we can notice that the growth of the overhead is consistent with the increment of the number of tasks per node for pilots with 256, 512 and 1024 worker nodes, and much less than linear for the pilot with 2048 worker nodes \aanote{Although that histogram is not trustworty because it is generate with only two runs.}

@@

The last experiments % deals with
study strong scalability by running the same amount of tasks for different pilot sizes. We used
% a number of AthenaMP instances equal to
2048 AthenaMP instances and % tested
pilots with 256, 512, 1024 and 2048 nodes. Thus, the number of AthenaMP generations is equal to eight times the size of the smallest pilot and corresponds to the size of the largest pilot. As a consequence, the number of consecutive generations of AthenaMP decreases with the pilot size by generating different dynamics within the pilots. This experiment aim to show that the pilot overhead is not affected by the concurrency level within the pilot but it depends only on the number of tasks.  
\mtnote{Not sure I understand this sentence}\aanote{My fault. It should have been seven and null or 8 and 1. It depends on how we consider the word sequential. anyway, to avoid confusion I changed the sentence.}. Each AthenaMP instance
simulates sixteen events as in the previous experiment.
